Unsupervised Learning for Identifying Events in Active Target Experiments

### 2020-08-06 doc/Manuscript/article.tex
Updates from Overleaf

\begin{figure}[tbh]
	\centering
	\includegraphics[width=.8\textwidth]{plots/mixae.pdf}
	\caption[Mixture of autoencoders schematic]{Schematic of a MIXAE model. A sample $\hat{\boldsymbol{x}}$ is compressed to set of lower-dimensional representations $\{\boldsymbol{z}^{(i)}\}$ by $N$ autoencoders. These samples are concatenated and passed through an auxiliary assignment network that predicts a confidence of cluster belonging for each autoencoder. For further details see the text. Figure adapted from \citet{Zhang}}
	\label{fig:mixae}
\end{figure}

@@

With the best set of hyperparameters, each highest performing model is thereafter run $10$ times\footnote{The MIXAE model is significantly more computationally expensive to train than a $K$-means model. Reulting in the skew in number of runs in the two cases.}. The results are listed in table \ref{tab:clstr_mixae}.
We observe that, while the algorithm can achieve a very strong performance, the performance varies. In some cases the MIXAE model converges to a seemingly good configuration, based on its unsupervised training goals. However, when inspecting its clustering performance against labelled data, the seemingly good model does no better than a model based on random selection. 
This happens more frequently with the raw data, indicating an interaction with the noise levels present in the events.

@@

VGGnet models are distributed freely with weights trained on the imagenet \cite{deng2009imagenet} image classification task. For the results in section \ref{sec:kmeans_results} we used a VGG16 model pre trained on imagenet data.

\begin{table}
\caption[vgg architectures]{Showing the details of the VGG network architectures. Network D trained on the ImageNet \cite{Russakovsky2015} data set the network known as  VGG16 and is what we use in this thesis.}\label{tab:vgg}
\includegraphics[width=\textwidth]{plots/vgg_architectures.png}
\end{table}

@@

In the MIXAE algorithm the hyper-parameters to adjust are all the ordinary parameters associated with a neueral network. We chose to base our neural network parameter choices on the VGG16 architecture. 
The parameters chosen for the autoencoders are listed in full in table \ref{tab:mixe_ae_hyperparams}.

>>>>

\begin{figure}[tbh]
	\centering
	\includegraphics[width=.8\textwidth]{plots/mixae.pdf}
	\caption[Mixture of autoencoders schematic]{Schematic of a MIXAE model. A sample $\hat{\boldsymbol{x}}$ is compressed to set of lower-dimensional representations $\{\boldsymbol{z}^{(i)}\}$ by $N$ autoencoders \cite{Zhang}. These samples are concatenated and passed through an auxiliary assignment network that predicts a confidence of cluster belonging for each autoencoder.}
	%For further details see the text. Figure adapted from \citet{Zhang}}
	\label{fig:mixae}
\end{figure}

@@

With the best set of hyperparameters, each highest performing model is thereafter run $10$ times\footnote{The MIXAE model is significantly more computationally expensive to train than a $K$-means model. Resulting in the skew in number of runs in the two cases.}. The results are listed in table \ref{tab:clstr_mixae}.
We observe that, while the algorithm can achieve a very strong performance, the performance varies. In some cases the MIXAE model converges to a seemingly good configuration, based on its unsupervised training goals. However, when inspecting its clustering performance against labelled data, the seemingly good model does no better than a model based on random selection. 
This happens more frequently with the raw data, indicating an interaction with the noise levels present in the events.

@@

VGGnet models are distributed freely with weights trained on the ImageNet \cite{deng2009imagenet} image classification task. For the results in section \ref{sec:kmeans_results} we used a VGG16 model pre trained on ImageNet data.

\begin{table}
\caption[vgg architectures]{Showing the details of the VGG network architectures. Network D trained on the ImageNet \cite{Russakovsky2015} data set the network known as  VGG16 and is what we use in this thesis. Table  }\label{tab:vgg}
\includegraphics[width=\textwidth]{plots/vgg_architectures.png}
\end{table}

@@

In the MIXAE algorithm the hyper-parameters to adjust are all the ordinary parameters associated with a neural network. We chose to base our neural network parameter choices on the VGG16 architecture. 
The parameters chosen for the autoencoders are listed in full in table \ref{tab:mixe_ae_hyperparams}.
